### 2021-02-03 research project/sections/Analysis_of_results.tex
rp

Where decimal places and iterations are compared, there is a clear difference between the two 
methods: Madhava's method indeed takes more iterations to converge to a specific decimal of 
the value $\pi$. However, in the second graph comparing time, it can be noted that Madhava's 
method is marginally faster until the decimal 20, when the two methods diverge. It could be 
assumed that this occurrence is due to differences between the types of the two methods. Madhava's 
method is what is called an alternating series, due to its nature of alternating between values in order 
to converge to a specific value, in this case $\pi$, while Viète's method is an infinite product. The 
difference between these two methods is underlined in (Figure 3) \ref{fig:comparaison}. It can be 
deduced that at lower decimal values Madhava's method is faster as Viète's method's approximation 
accuracy increases in what looks like an exponential fashion.

>>>>

Where decimal places and iterations are compared, there is a clear difference between the two 
methods: Madhava's method indeed takes more iterations to converge to a specific decimal of 
the value $\pi$. However, in the second graph comparing time, it can be noted that Madhava's 
method is marginally faster until the decimal 20, when the two methods diverge. It could be 
assumed that this occurrence is due to differences between the types of the two methods. Madhava's 
method is what is called an alternating series, due to its nature of alternating between values in order 
to converge to a specific value, in this case $\pi$, while Viète's method is an infinite product. The 
difference between these two methods is underlined in (Figure 3) \ref{fig:comparaison}. It can be 
deduced that at lower decimal values Madhava's method is faster as Viète's method's approximation 
accuracy firstly increases in what seems similar to a curve from an exponential function $f : x \to -2x^2$. 
It can also be said that while Madhava's method alternates between values such that $m_{n} > \pi, m_{n+1} < \pi$, 
Viète's method approaches pi in a way that the approximation is always $v < \pi$.
